%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage[pdftex]{hyperref}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Overleaf Example},
    pdfpagemode=FullScreen,
}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Demur Nodia} & Email : \href{mailto:demur.nodia@gmail.com}{\underline{demur.nodia@gmail.com}}\\ & @ \href{https://github.com/demonno}{\underline{Github}} @ \href{https://www.linkedin.com/in/demur-nodia}{\underline{Linkdin}} @ \href{https://twitter.com/demurnodia}{\underline{Twitter}} @ \href{https://stackoverflow.com/users/1448424/demonno}{\underline{StackOverflow}}
  
\end{tabular*}


\section{Summary}

Senior Software Engineer specialized in backend technologies. Interested in continues delivery, software architecture and functional programming. Open source projects contributor.

  \resumeSubHeadingListStart
    \resumeSubItem{F\#}{Implemented SDMX TypeProvider for \href{https://github.com/fsprojects/FSharp.Data/issues/1203}{\underline{FsharpData}}.}
    \resumeSubItem{Open Source}
      {Contributions to \href{https://github.com/django/django/pull/9993}{\underline{Django}}, \href{https://github.com/FactoryBoy/factory_boy/pull/368}{\underline{FactoryBoy}}, \href{https://github.com/namespace-ee/django-rest-framework-sideloading}{\underline{drf-siledloading}}}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\href{https://paxful.com}{\underline{Paxful}}}{Tallinn, Estonia}
      {Lead Software Engineer}{Tallinn, Estonia (Oct 2021 - Present(5 Months+)}
      \resumeItemListStart
        \resumeItem{Domain}
          {OAuth2 Service, API Gateway, SMS, Email, 2FA, OTP Services, internal  python libraries.}
        \resumeItem{Processes}
          {Following continues delivery approach while software development, using TDD. While having more than 12 servcices in scope, managed communication with other teams who, integrate with our services. Standardied CI/CD pipelines by making. Set and encouriged minimum code quality standards.}
      \resumeItemListEnd

\resumeSubheading
      {\href{https://paxful.com}{\underline{Paxful}}}{Tallinn, Estonia}
      {Senior Software Engineer}{Feb 2020 - May 2021 (1 year 3 months)}
      \resumeItemListStart
        \resumeItem{Domain}{While being part of the process towards transitioning to microservices architecture, I have worked on some of the fundamential services which solved issues related to unifing Localisation for all products in the company and provided support and guideines for integration. Developers portal and Internal administration tool built using django admin.}
        \resumeItem{Team}
          {As a member of an agile team(~8) has been involved in building and maintaining microservices in python, using async stack \textbf{python}, \textbf{FastAPI}, \textbf{Postgresql}.}
        \resumeItem{Infrastructure}
          {AWS, Kubernetes, Helm, Docker, Gitlab CI, Sentry, Elastic stack, prometheus and grafana.}
      \resumeItemListEnd
	
    \resumeSubheading
      {\href{https://namespace.ee}{\underline{Namespace}}}{Tallinn, Estonia}
      {Software Engineer}{Jun 2017 - Dec 2019 (2 years 7 months)}
      \resumeItemListStart
        \resumeItem{Domain}
          {Fleet tracking/management. Real time vehicle tracking and data processing. Reporting and management software.}
		\resumeItem{Stack}
          {Worked on backend technologies, \textbf{Python, Django, Postgresql, PostGIS, Redis, Spark, Scala, Kafka.}}
      \resumeItemListEnd

    \resumeSubheading
      {\href{http://innotec.ge/}{\underline{Innotec}}}{Georgia, Tbilisi}
      {Software Developer/ Team Lead}{May 2011 - Jul 2016 (5 years 3 months)}
      \resumeItemListStart
        \resumeItem{Domain}
          {Worked on building software for Banking, Insurance, Transportation, Advertising industries. Was involved in full sycle of softwere development started from meetings with clients, setting up technical assignments }
        \resumeItem{Stack}
          {\textbf{Java, Hibernate, Spring, Python, Django, Android}}
      \resumeItemListEnd
      
     \resumeSubheading
      {\href{https://www.facebook.com/unihackge/}{\underline{Unihack}}}{Georgia, Tbilisi}
      {Co-Founder, Co-Organizer}{Dec 2013 - Dec 2015}

		Contribution with team of 6 towards the community building and introducing hackathon cultion in the region.

     \textbf{HackTbilisi}{: Dec 2015 \href{https://www.facebook.com/events/684989148311419/}{\underline{2015f.hacktbilisi.com}}}
     \hfill
     \textbf{hack@MACS}{: Mar 2014 \href{https://www.facebook.com/events/449121528548787/}{\underline{macs.unihack.ge}}}
     
     \textbf{HackTbilisi}{: Dec 2014 \href{https://www.facebook.com/events/580741565385417/}{\underline{2014f.hacktbilisi.com}}}
     \hfill
     \textbf{hack@CST}{: Mar 2013  \href{https://www.facebook.com/events/534752266617343/}{\underline{cst.unihack.ge}}}	
	
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Masters Thesis}
      { \href{https://github.com/demonno/ttu-thesis/blob/master/thesis_tex/masters-thesis.pdf}{\underline{SDMX Type Providef for F\#}}}
  \resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {UT/TalTech – University of Tartu/Tallinn University of Technology}{Tartu/Tallinn, Estonia}
      {Master’s Degree, Software Engineering}{Sept. 2016 – Jul. 2018}
    \resumeSubheading
      {Caucasus University}{Tbilisi, Georgia}
      {Bachelor’s Degree, Bachelor of Engineering in Informatics}{Sep 2010 – Jul 2015}
    \resumeSubheading
      {Upper Austria University of Applied Sciences}{Linz, Austria}
      {Bachelor's degree, Media Technology Design}{Sep 2012 – Feb 2013}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
