%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage[pdftex]{hyperref}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={CV/Resume - Demur Nodia},
    pdfpagemode=FullScreen,
}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    #1 \vspace{-2pt}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\link}[2]{\href{#1}{\underline{#2}}}


%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Demur Nodia} & Email : \href{mailto:demur.nodia@gmail.com}{\underline{demur.nodia@gmail.com}}\\ & @ \href{https://github.com/demonno}{\underline{Github}} @ \href{https://www.linkedin.com/in/demur-nodia}{\underline{Linkdin}} @ \href{https://twitter.com/demurnodia}{\underline{Twitter}} @ \href{https://stackoverflow.com/users/1448424/demonno}{\underline{StackOverflow}}
  
\end{tabular*}


\section{Summary}
Backend-focused Software Engineer passionate about scalable architecture, functional programming, and continuous delivery. Experienced in designing high-performance, maintainable systems with clean code, unit testing, and refactoring best practices.


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\link{https://pv0.one}{PV0.ONE}}{Remote}
      {Software Engineer}{Mar 2023 - Present (2 years+)}
      \resumeItemListStart
        \resumeItem{Joined as the 2nd engineer at an early-stage financial blockchain startup building a debt capital market platform for issuing government and corporate bonds on Ethereum blockchains.}           
        \resumeItem{Contributed to full-stack product development, later specializing in backend systems and blockchain APIs.}
        \resumeItem{Tech stack: \textbf{AWS, Python, Django, HTMX, Typescript, Hardhat, Solidity, PostgreSQL, Kubernetes, Helm, Docker, Github(Actions), Sentry, Elastic Stack, Prometheus, Grafana.}.}
      \resumeItemListEnd
      
    \resumeSubheading
      {\link{https://paxful.com}{Paxful}}{Tallinn, Estonia}
      {Senior Software Engineer → Lead Software Engineer}{Feb 2020 - Mar 2023 (3 year 1 months+)}
      \resumeItemListStart
        \resumeItem{Maintained the technical backlog and roadmap, ensuring seamless project execution.}
        \resumeItem{Led the standardization of development workflows across 20+ microservices, improving scalability and reducing onboarding time for new engineers.}
        \resumeItem{Built \link{http://accounts.paxful.com/}{OAuth2 Service},  \link{https://developers.paxful.com/}{Developers portal}, \link{https://api.paxful.com/}{API Gateway}, enabling seamless integrations and enhancing developer experience.}  
        \resumeItem{Tech stack: \textbf{Python, FastAPI, Django, PostgreSQL, OpenAPI, AWS, Kubernetes, Helm, Docker, GitLab CI/CD, Sentry, Elastic Stack, Prometheus, Grafana.}.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{http://applysis.io}{\underline{Applysis}}}{Tallinn, Estonia}
      {Co-Founder}{Apr 2020 - Jul 20 (1 year 9 months)}
      \resumeItemListStart
        \resumeItem{Led Lean AI-based product development (\link{https://www.producthunt.com/products/applysis}{Product Hunt Campaign}}).
        \resumeItem{Completed\link{https://www.startupincubator.ee/}{startupincubator}} program, refining the product and business model.
      \resumeItemListEnd

    \resumeSubheading
      {\link{https://namespace.ee}{Namespace}}{Tallinn, Estonia}
      {Software Engineer}{Jun 2017 - Dec 2019 (2 years 7 months)}
      \resumeItemListStart
        \resumeItem{Developed fleet tracking and management software, including real-time vehicle tracking and reporting. Maintained public and internal APIs, refactored legacy code, and implemented new features.}
		\resumeItem{Tech stack: \textbf{Python, Django, Postgresql, PostGIS, Redis, Spark, Scala, Kafka, Github.}}
      \resumeItemListEnd

    \resumeSubheading
      {\href{http://innotec.ge/}{\underline{Innotec}}}{Tbilisi, Georgia}
      {Software Developer → Team Lead}{May 2011 - Jul 2016 (5 years 3 months)}
      \resumeItemListStart
        \resumeItem{Led full-cycle software development across banking, insurance, transportation, and advertising domains.}
        \resumeItem{Tech stack: \textbf{Java, Hibernate, Spring, Python, Django, Javascript, Android, Linux, Windows}.}
      \resumeItemListEnd      
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Masters Thesis}
      { \link{https://github.com/demonno/ttu-thesis/blob/master/thesis_tex/masters-thesis.pdf}{SDMX Type Provider for F\#}}
    \resumeSubItem{F\# →}{Implemented SDMX TypeProvider for \href{https://github.com/fsprojects/FSharp.Data/issues/1203}{\underline{FsharpData}} enabling streamlined data access in F\# projects.}
    \resumeSubItem{Open Source →}
      {Contributions to \link{https://github.com/localstack/localstack/pull/7055}{{LocalStack}}, \link{https://github.com/django/django/pull/9993}{{Django}}, \link{https://github.com/FactoryBoy/factory_boy/pull/368}{{FactoryBoy}}, \link{https://github.com/namespace-ee/django-rest-framework-sideloading}{drf-sideloading}}.
  \resumeSubHeadingListEnd



%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {UT/TalTech – University of Tartu/Tallinn University of Technology}{Tartu/Tallinn, Estonia}
      {Master’s Degree, Software Engineering}{Sep 2016 – Jul 2018}
    \resumeSubheading
      {Caucasus University}{Tbilisi, Georgia}
      {Bachelor’s Degree, Bachelor of Engineering in Informatics}{Sep 2010 – Jul 2015}
    \resumeSubheading
      {Upper Austria University of Applied Sciences}{Linz, Austria}
      {Bachelor's degree, Media Technology Design}{Sep 2012 – Feb 2013}
  \resumeSubHeadingListEnd

%-------------------------------------------

\textit{Source of this resume is available at} \link{https://github.com/demonno/resume}{github.com/demonno/resume}

\end{document}
